Output Summary

### 2021-09-21 03-post-process/output-plots.Rmd
Update boxplots showing main parameter estimates for ocean survival

  # replace the summary stats with my preferred quantiles
  par(mar = c(2,3,1,1), mgp = c(2,0.35,0), tcl = -0.15)
  bp$stats = apply(post_sub, 2, function(x) quantile(x, c(0.025, 0.25, 0.5, 0.75, 0.975)))
  bxp(bp, ylab = ylab, xlab = "", outline = FALSE, ylim = ylim, ...,
      staplelty = 0, whisklty = 1, boxfill = boxfill, boxcol = border, medcol = border, whiskcol = border)
} 
```

@@

### Year 1

```{r yr1-ocean-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot(sub_index("mu_phi_O0_O1[origin]", origin = "."), ticklabs = c("NOR", "HOR"), ylim = c(0,1), ylab = "Average Survival")
my_boxplot("sig_Lphi_O0_O1", ylab = "Process SD")
```

### Year 2

```{r yr2-ocean-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot(sub_index("mu_phi_O1_O2[origin]", origin = "."), ticklabs = c("NOR", "HOR"), ylim = c(0,1), ylab = "Average Survival")
my_boxplot("sig_Lphi_O1_O2", ylab = "Process SD")
```

>>>>

  # replace the summary stats with my preferred quantiles
  par(mar = c(5,3,1,1), mgp = c(2,0.35,0), tcl = -0.15)
  bp$stats = apply(post_sub, 2, function(x) quantile(x, c(0.025, 0.25, 0.5, 0.75, 0.975)))
  bxp(bp, ylab = ylab, xlab = "", outline = FALSE, ylim = ylim, ...,
      staplelty = 0, whisklty = 1, boxfill = boxfill, boxcol = border, medcol = border, whiskcol = border)
} 
```

@@

### Year 1 {.tabset .tabset-pills}

#### Mean

```{r yr1-ocean-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot(sub_index("mu_phi_O0_O1[origin,pop]", origin = o_nor, pop = "."), main = "NOR", ylim = c(0,1), ylab = "Average Survival")
my_boxplot(sub_index("mu_phi_O0_O1[origin,pop]", origin = o_hor, pop = "."), main = "HOR", ylim = c(0,1), ylab = "Average Survival")
```

#### Process SD and Correlation

```{r yr1-ocean-bxp2, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,3))
my_boxplot(sub_index("sig_Lphi_O0_O1[pop]", pop = "."), ylab = "Process SD")
my_boxplot(sub_index("kappa_phi_O0_O1[pop]", pop = "."), ylab = "Autocorrelation")
my_boxplot("rho_Lphi_O0_O1[", ticklabs = vcov_labels, ylab = "Among Population Correlation", ylim = c(-1,1), las = 2)
```

### Year 2 {.tabset .tabset-pills}

```{r yr2-ocean-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot(sub_index("mu_phi_O1_O2[origin,pop]", origin = o_nor, pop = "."), main = "NOR", ylim = c(0,1), ylab = "Average Survival")
my_boxplot(sub_index("mu_phi_O1_O2[origin,pop]", origin = o_hor, pop = "."), main = "HOR", ylim = c(0,1), ylab = "Average Survival")
```

### Year 3 {.tabset .tabset-pills}

```{r yr3-ocean-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot(sub_index("mu_phi_O2_O3[origin,pop]", origin = o_nor, pop = "."), main = "NOR", ylim = c(0,1), ylab = "Average Survival")
my_boxplot(sub_index("mu_phi_O2_O3[origin,pop]", origin = o_hor, pop = "."), main = "HOR", ylim = c(0,1), ylab = "Average Survival")
```

### NOR:HOR Log Odds Ratio

```{r ocean-surv-scaler, fig.width = 8, fig.height = 3.5}
my_boxplot(sub_index("O_phi_scaler_nat_hat[pop]", pop = "."), ylab = "Log Odds Ratio")
```
